---
title: "ALEC Analysis"
format: html
editor: visual
---

These are data from Francis Prevatt.

Students with ADHD

Control Students (without ADHD diagnosis)

Measures of ADHD Symptoms (hyperactivity, inattention)

Measures of anxiety & panic

SAT, ACT scores

Year, Age, Gender, ...

```{r}
Alec <- read.csv("/cloud/project/PrevattData/AlecSubset.csv")
Alec
```

## Find missing data patterns

```{r}
library(Amelia)
missmap(Alec)
```

## Break variables into groups

```{r}
demographics <- c("group","ID","YEAR","AGE","GENDER","ETHNICITY")
satACT <- c("SAT","SATVERBAL","SATQUANT","SATWRIT","ACT","ACTSCOREENG","ACTSCOREMATH","ACTSCOREREAD","ACTSCORESCIE","ACTSCORECOMP")
psych <- c("PSYCHOEDASSE","DIAGNOSEDLD","DIAGNADHD","DIAGNOTHER","SPECIALED","ADHDEFindex")
nonCog <-c("Acadmeicskills","inter_motivation","Instruc_efficacy","Concentration","Exter_motiv_fut","Socializing","Career_decide","Person_Adjust","Exter_Motiv_Curr")
anxiety <- c("GADG","GADD","PAG","genanxa","paa","adhdtot","allanx","adhdxanx","inatt","hyper","inattxanx","hyperxanx","Lack_Anxiety")
missmap(Alec[,demographics],main="Alec demographics")
missmap(Alec[,satACT],main="Alec SAT & ACT")
missmap(Alec[,psych],main="Alec Psych Measures")
missmap(Alec[,nonCog],main="Alec Non Cognitive Measures")
missmap(Alec[,anxiety],main="Alec Aniexty, Panic & ADHD")
```

## Anxiety and Panic by Group

Make sure factor variables are marked as factors.

```{r}
Alec$group <- factor(Alec$group,levels=1:2,labels=c("ADHD","Control"))
Alec$YEAR <- factor(Alec$YEAR,levels=1:5,labels=c("Freshman","Sophmore","Junior","Senior","Grad"))
Alec$GENDER <- factor(Alec$GENDER,levels=1:2,labels=c("Female","Male"))
Alec$ETHNICITY <- factor(Alec$ETHNICITY)
summary(Alec[c("group","YEAR","GENDER","ETHNICITY")])
                     
```

## Look at Anxiety by Diagnosis

```{r}

ggplot(Alec,aes(y=genanxa,group=group)) + geom_boxplot()
```

```{r t-test-completecase}
fitcom <- lm(genanxa~group,data=Alec,na.action=na.omit)
summary(fitcom)
```

## Build missing model for Genanxa

```{r}
cor(Alec[,satACT],Alec$genanxa,use="complete")
cor(Alec[,psych],Alec$genanxa,use="complete")
cor(Alec[,anxiety],Alec$genanxa,use="pair")
```

See if these variables are collected (missing) inpendently of genanxa.

```{r}
missmap(Alec[is.na(Alec$genanxa),anxiety])
missmap(Alec[is.na(Alec$genanxa),satACT])
missmap(Alec[is.na(Alec$genanxa),psych])
```

Fit some models

```{r}
fit.genanxa.miss <- lm(genanxa~YEAR+GENDER+inatt+hyper +ETHNICITY,
                       data=Alec,na.action=na.exclude)
summary(fit.genanxa.miss)
```

No need to drop non-significant variables from model.

Imputation model should always include all of the variables in the analysis model.

## Make predictions

```{r}
genanxa.pred <- predict(fit.genanxa.miss,newdata=Alec,
                        na.action=na.pass)
sum(is.na(Alec$genanxa))
sum(is.na(genanxa.pred))
sum(is.na(Alec$genanxa) & is.na(genanxa.pred))
Alec$genanxa.imp <- ifelse(is.na(Alec$genanxa),genanxa.pred,Alec$genanxa)

```

## Redo analyses

```{r}
ggplot(Alec,aes(y=genanxa,group=group)) + geom_boxplot()
ggplot(Alec,aes(y=genanxa.imp,group=group)) + geom_boxplot()
```

```{r t-test-imp}
fitcom1 <- lm(genanxa.imp~group,data=Alec,na.action=na.omit)
summary(fitcom)
```

```{r compare models}
coef(fitcom)
coef(fitcom1)
```
